---
title: "MHA_no_response data analysis"
format: html
editor: visual
---

# Load Packages:

```{r, message= FALSE}
library(readr)
library(tidyr)
library(dplyr)
library(DT)
library(arrow)
library(bayestestR)
library(gt)
library(gtsummary)
library(ggplot2)
library(stringr)
library(dplyr)
library(broom.helpers)
library(insight)
library(readxl)
```

# 1. Long_prompt_motivation:

## Read-in the data:

Let's start with reading in the data each by each：

```{r, warning = FALSE}
df1 <- read_xlsx(('data_new/Long_Prompt_Motivation_Prototype_2.xlsx'))
```

## this is for all the data

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(long_prompt_motivation_prototype_2_longpromptmotivreward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```

## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(long_prompt_motivation_prototype_2_longpromptmotivreward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```

## now group them by people who people who respond 
# 2. Long_Prompt_Rationale_Prototype 

```{r, warning = FALSE}
df1 <- read_xlsx(('data_new/Long_Prompt_Rationale_Prototype_2.xlsx'))
```

## this is for all the data
```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(long_prompt_rationale_prototype_2_longpromptrationalereward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```
## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(long_prompt_rationale_prototype_2_longpromptrationalereward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```


# 3. Long_Prompt_ReflectionCommit_Prototype

## Read-in the data:

Let's start with reading in the data each by each：

```{r, warning = FALSE}
df1 <- read_xlsx(('data_new/Long_Prompt_ReflectionCommit_Prototype_2.xlsx'))
```

## this is for all the data

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(long_prompt_reflectioncommit_prototype_2_longpromptcommitreward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```

## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(long_prompt_reflectioncommit_prototype_2_longpromptcommitreward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```


# 4. Long_prompt_Reminder_Prototype

## Read-in the data:

Let's start with reading in the data each by each：

```{r, warning = FALSE}
df1 <- read_xlsx(('data_new/Long_prompt_Reminder_Prototype_2.xlsx'))
```

## this is for all the data

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(long_prompt_reminder_prototype_2_longpromptreminderreward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```

## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(long_prompt_reminder_prototype_2_longpromptreminderreward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```


# 5. MHAwave1ModularRationale

## Read-in the data:

Let's start with reading in the data each by each：

```{r, warning = FALSE}
df1 <- read_xlsx(('data_new/MHAwave1ModularRationale.xlsx'))
```

## this is for all the data

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(MHAwave1ModularMessageReward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```

## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(MHAwave1ModularMessageReward)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```


# 6. Modular_Interaction_MHA_Prototype

## Read-in the data:

Let's start with reading in the data each by each：

```{r, warning = FALSE}
df1 <- read_xlsx(('data_new/Modular_Interaction_MHA_Prototype.xlsx'))
```

## this is for all the data

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(modular_interaction_mha_prototype_interactionrating)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```

## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(modular_interaction_mha_prototype_interactionrating)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```


# 7.Modular_Link_MHA_Prototype

## Read-in the data:

Let's start with reading in the data each by each：

```{r, warning = FALSE}
df1 <- read_xlsx('data_new/Modular_Link_MHA_Prototype.xlsx')
```

## this is for all the data

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  summarise(responded = (sum(!is.na(modular_link_mha_prototype_linkrating)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 

```

## this is for data that starting from January:

```{r, warning = FALSE, message= FALSE}
df1 |>
  group_by(learner, arm) |>
  mutate(date_arm_assign = as.Date.character(arm_assign_time)) |>
  filter(date_arm_assign > '2023-01-01') |>
  summarise(responded = (sum(!is.na(modular_link_mha_prototype_linkrating)) > 0)) |>
  tbl_cross(row = "arm", col = "responded", percent = c("row")) 
```
